\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=7pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Ioannis Kyriazis}

\vspace{5pt}

% contact information
\centerline{\href{mailto:yiannisgr1@gmail.com}{yiannisgr1@gmail.com} | \href{https://ioannis.ky}{ioannis.ky} | \href{https://github.com/ikyriazis}{github.com/ikyriazis}}

\vspace{-10pt}

% skills section
\section*{Skills}
\textbf{Languages:} JavaScript, Java, Python, SQL, C, C++, C\# \\
\textbf{Frameworks:} Node.js, React, React Native, Angular, Svelte, Astro, Spring Boot \\
\textbf{Tooling:} git, Docker, Kubernetes, Airflow, Jenkins, Shell, nginx, Swagger \\
\textbf{Databases:} MySQL, MongoDB, Postgres, Redis, ElasticSearch, GraphQL


\vspace{-6.5pt}

% experience section
\section*{Experience}
\textbf{Senior Software Engineer,} {VRSCO} -- Worcester, MA \hfill May 2023 -- Present \\
\vspace{-9pt}
\begin{itemize}
  \item Architected and deployed a highly scalable cloud infrastructure using nginx, Linode, pm2, and Cloudflare that handles 195K+ monthly requests, ensuring 99.9\% uptime.
  \item Designed, developed, and published a cross‐platform app (iOS and Android) using React Native that includes QR code registration, multi‐platform sign‐in, email verification, and real-time messaging for item recovery.
  \item Developed a secure backend server using Node.js and MySQL featuring real‐time chat via WebSockets, robust and secure password management, automated email notifications, and integrated payment processing.
  \item Overhauled the existing React e-commerce site using Astro and Svelte to improve performance and aesthetic. Features dynamic product display, cart logic, and secure Stripe integration.
  \item Integrated Endato API on e-commerce site to provide a free privacy test to prospects to increase engagement.
\end{itemize}

\textbf{Software Engineer,} {UnitedHealth Group} -- Boston, MA \hfill June 2021 -- May 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Streamlined the data ingestion process for 5K+ repositories across three datastores, automating work flows using Airflow and reducing runtime and data consumption by 90\% through delta processing.
  \item Optimized data pipelines via horizontal scaling with the Dask Python library, cutting down process by 10x.
  \item Refactored legacy table web component to local component and integrated within Angular project.
  \item Added frontend capabilities to sort/filter data and generate Excel files using Angular, NG Prime, and SheetJS.
  \item Designed, implemented and published APIs using Swagger and Spring Boot to share data with external teams.
  \item Built and deployed API Docker containers to Kubernetes using Jenkins to ensure robustness and scalability.
  \item Wrote a Python script to generate JWTs for API testing to cut out 3 of 5 steps and led to team-wide adoption.
  
\end{itemize}

% \textbf{Job Title,} \href{https://www.fstl1992.com/}{Company} -- City, ST \hfill XXXX -- XXXX \\
% \vspace{-9pt}

\vspace{-18.5pt}

% projects section
\section*{Projects}
\textbf{Solfege Mental Model Game} \hfill \href{https://dofalare.com}{dofalare.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Built full stack web application with Astro, Svelte, Node.js, Javascript, and MySQL to allow users to practice their mental model of the solfege system with easy and hard mode.
  \item Automatically calculate and display user game statistics and allow users to submit their name along with their score to the public leaderboard.
\end{itemize}

\textbf{CanvasKicks Portfolio Page} \hfill \href{https://canvaskicks.store/prevWorks.html}{canvaskicks.store} \\
\vspace{-9pt}
\begin{itemize}
  \item Built secure admin dashboard which includes custom CMS to support automatic post creation and message inbox from potential clients using HTML, CSS, JavaScript, MongoDB, and Node.js.
  \item Facilitated safe community interactions by only allowing authenticated users to submit comments.
\end{itemize}

\textbf{Hospital Kiosk Application} \hfill \href{https://github.com/IKyriazis/BWHKioskApp/commits?author=IKyriazis}{github.com/IKyriazis/BWHKioskApp} \\
\vspace{-9pt}
\begin{itemize}
  \item Achieved best application in the class competition to apply Agile development methodologies and design patterns in Java to create a pathfinding kiosk application, map builder, room scheduler, etc.
  \item Implemented two‐factor authentication, RFID card authentication using Arduino and integrating with app via serial communication, salt/hashed password storage, and an internal transportation request menu.
\end{itemize}

% alternate formatting for projects section
% \section*{Projects}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}

\vspace{-18.5pt}

% education section
\section*{Education}
\textbf{Worcester Polytechnic Institute} -- BS: Computer Science, Minors: Electrical Eng., Prof. Writing \hfill May 2021

\end{document}
