%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {CEO} % Job title
    {VRSCO - www.vrsco.chat - check it out!} % Organization
    {Worcester, MA} % Location
    {January 2022 – Present}
    {
      \begin{cvitems} % Descriptions of tasks/responsibilities
      \item {Raised over \$90k of seed capital and amassed international user base consisting of over 50 users.}
      \item {Devised processes to manufacture VRSCO tags out of aluminum for less than \$0.25 each tag, produced more than 200 tags.}
      \item {Designed, developed, and published a mobile app for iOS and Android with features like QR code registration, multi-platform sign-in, email verification, and messaging for lost item recovery.}
      \item {Created a server backend with real-time chat using websockets, secure password management, email sending, and payment processing.}
      \item {Configured cloud infrastructure to host databases, frontend, and backend components, handles 2K unique visitors and 20K requests a month.}
      \item {Developed an ecommerce frontend in React with components for dynamic product display, a shopping cart, and secure payment processing.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer} % Job title
    {Optum} % Organisation
    {Boston, MA} % Location
    {June 2022 – May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and deployed an Airflow Directed Acyclic Graph (DAG) to orchestrate the data collection process from diverse data stores.}
        \item {Extracted data from MySQL, OrientDB, and Elasticsearch databases using Extract-Transform-Load (ETL) techniques.}
        \item {Provided stakeholders with valuable business insights extracted from processed data to make informed decisions.}
        \item {Rewrote a critical step of the ingestion process for all GitHub repositories in the organization.}
        \item {Developed a parsing solution to extract critical information, including the package name of Java, Groovy, and C\# files from all repos.}
        \item {Refactored the ingestion process to implement delta processing, ensuring updates only occur for repositories modified since the last run.}
        \item {Optimized process through vertical and horizontal scaling to cut run time by 10x using Dask python library.}
      \end{cvitems}
    }
  \cventry
    {Technology Development Program Associate} % Job title
    {} % Organisation
    {} % Location
    {June 2021 – June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced the user interface of Tech360, a critical business application, using Angular and NG Prime.}
        \item {Refactored web components of Hardware Padu page into local components to allow filtering and exportation of data.}
        \item {Added frontend capabilities to filter and export data of Hardware Padu page.}
        \item {Designed, implemented and published robust APIs using Swagger and Spring Boot to provide other teams in the organization with PLM BSI data.}
        \item {Crafted MySQL statements to execute within API to retrieve and update tables within my team's database.}
        \item {Implemented functionality to filter data retrieved according to parameters set by user.}
        \item {Helped external teams generate credentials through API management system so that they may access our team's APIs.}
        \item {Built and deployed docker containers of Spring Boot APIs to Kubernetes using Jenkins.}
        \item {Eliminated 3 out of 5 steps for testing APIs by writing python script that generates JWTs.}
      \end{cvitems}
    }

\end{cventries}
