%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Solfege Mental Model Game} % Organisation
    {dofalare.com} % Project
    {Thessaloniki, Greece} % Location
    {May - June 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
   \item {Built full stack web application with Astro, Svelte, NodeJS, JavaScript, and MySQL to allow users to practice their mental model of the solfege system with easy and hard mode.}
       \item {Automatically calculate and display user game statistics and allow users to submit their name along with their score to the public leaderboard.}
      \end{cvitems}
    }
\cventry
    {Canvas Kicks} % Organisation
    {Artist Portfolio Page} % Project
    {Worcester, MA} % Location
    {March - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
       \item {Built secure admin dashboard which includes custom CMS to support automatic post creation and message inbox from potential clients.}
       \item {Facilitated safe community interactions by allowing authenticated users to comment on any post.}
      \end{cvitems}
    }


  \cventry
    {Worcester Polytechnic Institute} % Organisation
    {Hospital Kiosk Application } % Project
    {Worcester, MA} % Location
    {March - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
       \item {Achieved best application in the first and second iterations of class competition to apply Agile development methodologies and
        design patterns in Java to create a pathfinding kiosk application, map builder, room scheduler, etc.}
        \item {Gathered software requirements by surveying, brainstorming, creating user stories, scenarios and storyboards.}
        \item {Implemented two-factor authentication, RFID card authentication, salt/hashed password storage, and an internal transportation request menu.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Worcester Polytechnic Institute} % Organisation
    {The Maria Amor Foundation: A Case Study on Holistic Healing} % Project
    {Cuenca, Ecuador} % Location
    {October - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Facilitated weekly sponsor meetings and interviewed female victims of domestic abuse in Spanish.}
        \item {Managed and operated filming equipment to capture data from
        interviews and optimized interview transcription process for rapid analysis.}
        \item {Produced 5 videos that showcase the unique ecologically sustainable aspects of our sponsor.}
        \item {Followed
        Strunk's Elements of Style to edit final report for clarity, concision, and cohesiveness.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
